\documentclass{article}
\title{SAT-Solver}
\author{Tao Lin, EECS, PKU, 1600012773}
\usepackage{geometry}
\geometry{scale=0.70,top=2cm, bottom=2cm}
\begin{document}
	
	\maketitle

	\textbf{DPLL Algorithm}
	
	In every step, continuously apply BCP and SET\_PURE\_TRUE to simplying the formula, then choose one variable, respectively set it to True and False and recursively move to next step, until a conflict occurs or the formula is satisfied.

	\textbf{Data Structure}
	\begin{enumerate}
		\item a list $F$ of sets to represent the CNF. $F[j]$ is the $j$th clause, which is a set of literals.
		\item a set $I$ of indexes to record the left clauses. $I = \{ j | F[j] \ne \top\}$.
		\item a hash map $S$ which maps literal $x$ to the clauses $x$ is in, implemented by a dict. $S[x] = \{j | x \in F[j]\}$
		\item a set $T$ of literals that can be True. In BCP, every unit clause provides such a literal, $T_1 = \{x|\exists j, |F[j]|=1, x \in F[j]\}$; in SPT, consider $x$ and its negation $-x$, $T_2 = \{x| |S[x]|>0, |S[-x]|=0\}$.$T = T_1 \cup T_2$.
	\end{enumerate}

	\textbf{Key Ideas}
	\begin{enumerate}
		\item \textbf{See BCP and SPT as a whole.} Except for choosing variables, they treat variables the same way: set to True or False, until no variable can be determined. $T$ is shared by them.
		\item \textbf{Choose variables greedily and randomly.} Greedily: clauses of smaller size are more decisive and variables occuring more often are more influential. Therefore, from the smallest clauses, choose a literal with the greatest $\alpha  |S[-x]| + \beta |S[x]|$. $\alpha$ and $\beta$ are weights, respectively set to 1.0 and 1.0 based on experiment. Randomly: experiment reveals that when there are too many clauses sharing the smallest size, greedy method fails, so randomly pick a literal instead. Set the chosen literal to True first.
		\item \textbf{Modify $F, I, S, T$ dynamically in assignment.} When setting literal $x_0$ to True, remove all the clauses which contain $x_0$, by deleting indexes from $I$ and from $S[x]$ for $x$ in deleted clauses; remove $-x_0$ from its clauses. Use the size of $F[j]$ to decide unit clause, use the sizes of $S[x]$ and $S[-x]$ to find pure literal.
		\item \textbf{Undo assignment.} The opposite of assignment. Undo assignment to regain $F, I, S$ instead of to reconstruct them.
		After assigning $x_0$, $F[j]$ that contain $x_0$, $S[x_0]$ and $S[-x_0]$ will never change, so they can be used when undoing.
		After a failing new step, undo the decision. 
		BCP and SPT should record the sequence of chosen literals, and undo in opposite order before return. 
		\item \textbf{Deal with $T$.} The set $T$ of literals which can be True is ignored when undoing.
		After BCP and SPT, $T$ becomes empty.
		After assigning $x_0$ and in the new step, $T$ changes. 
		When assigning $-x_0$, $T$ is useless, thus, empty $T$ before assigning $-x_0$. 
		\item \textbf{Return.}
		Return Unsat if $F[j]=\{\}$ is found when setting literals; or contradictory assignment is found in BCP and SPT.
		Return Sat if BCP and SPT return an empty $I$.
	\end{enumerate}

\end{document}
